---
title: "Data Analysis overview of Telangana Tourism"
author: "By Nitin Madas, Kaushal Joshi"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Telangana
![][telangana_intro]


# Data Description
![][data_desc]

```{r include=FALSE}
# Load required libraries
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
```
```{r eval=FALSE}
# Getting data from different csv files and combining them into one file

input_path = './%s_%s.csv'

domestic_path = 'domestic_visitors/domestic_visitors'
foreign_path = 'foreign_visitors/foreign_visitors'

all_domestic_data <- data.frame()
all_foreign_data <- data.frame()


for( year in years){
  file_path_domestic = sprintf(input_path, domestic_path, year)
  all_domestic_data =  rbind(all_domestic_data, read.csv(file_path_domestic))
  
  file_path_foreign = sprintf(input_path, foreign_path, year)
  all_foreign_data =  rbind(all_foreign_data, read.csv(file_path_foreign))
  
}

output_path = './%s.csv'

write.csv(all_domestic_data, sprintf(output_path, domestic_path), row.names=F)
write.csv(all_foreign_data, sprintf(output_path, foreign_path), row.names=F)


```
```{r}
# Loading data sets
domestic_vis = read.csv('./domestic_visitors/domestic_visitors.csv')
foreign_vis = read.csv('./foreign_visitors/foreign_visitors.csv')

head(domestic_vis)
head(foreign_vis)
```



# Data Cleaning
``` {r include=FALSE}
total_val = nrow(domestic_vis)
null_val = sum(is.na(domestic_vis))
percent = null_val/total_val *100

total_val_fore = nrow(foreign_vis)
null_val_fore = sum(is.na(foreign_vis))
percent_fore = null_val_fore/total_val_fore *100
```
#### In Domestic visitors, There are **`r null_val`** Null Values out of **`r total_val`** Values   
#### So, there are **`r  round(percent,2)`%** Null values

#### In Foreign visitors, There are **`r null_val_fore`** Null Values out of **`r total_val_fore`** Values   
#### So, there are **`r  round(percent_fore,2)`%** Null values
```{r warning=FALSE}
# Lets try to understand where these null values reside in our data
null_vis <- domestic_vis[is.na(domestic_vis$visitors), ]


# Group the data and count occurrences
count_data <- null_vis %>%
  group_by(district, year) %>%
  summarize(count = n())

# count_data %>% as_tibble() %>% print(n=40)


# Create the stacked bar plot
dom_plot = ggplot(count_data, aes(x = district, y = count, fill = as.factor(year)  ) )+
  geom_bar(stat = "identity",color = "black") +
    geom_text(aes(label = count, group = year), position = position_stack(vjust = 0.5)) +
  scale_y_continuous(breaks = seq(0, 50, by = 12)) +

  labs(x = "District", y = "Count", title = "Domestic Missing Values") +
  scale_fill_discrete(name = "Year") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Lets try to understand where these null values reside in our data
null_vis_fore <- foreign_vis[is.na(foreign_vis$visitors), ]


# Group the data and count occurrences
count_data_fore <- null_vis_fore %>%
  group_by(district, year) %>%
  summarize(count = n())

fore_plot = ggplot(count_data_fore, aes(x = district, y = count, fill = as.factor(year)  ) )+
  geom_bar(stat = "identity",color = "black") +
    geom_text(aes(label = count, group = year), position = position_stack(vjust = 0.5)) +
  scale_y_continuous(breaks = seq(0, 50, by = 12)) +

  labs(x = "District", y = "Count", title = "Foreign Missing Values") +
  scale_fill_discrete(name = "Year") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

dom_plot
fore_plot


```

#### Cleaning and Imputing the significant values
```{r}
calculate_missing_percentage <- function(data, group_columns, value_column) {
  # Calculate missing values per specified group columns
  missing_data <- data %>% 
    group_by(across(all_of(group_columns))) %>% 
    summarize(
      total_rows = n(),
      missing_values = sum(is.na({{ value_column }}))
    )
  
  # Calculate missing percentage
  missing_data <- missing_data %>%
    mutate(missing_percentage = (missing_values / total_rows) * 100)
  
  # Filter rows with missing percentage equal to 100%
  missing_all_values <- missing_data %>%
    filter(missing_percentage >25)
  
  return(missing_all_values)
}
```
```{r}
result_district <- calculate_missing_percentage(domestic_vis, c("district"), visitors)
result_foreign <- calculate_missing_percentage(foreign_vis, c("district"), visitors)
result_district_year_month <- calculate_missing_percentage(domestic_vis, c("month","year"), visitors)
result_district
result_foreign
```
#### We will delete the insignificant districts from the data i.e. districts which has more than 75% missing values
```{r}
districts_above_threshold_d <- result_district %>%
  filter(missing_percentage >= 75) %>%
  pull(district)  # Get the list of districts to remove for domestic_vis

districts_above_threshold_f <- result_foreign %>%
  filter(missing_percentage >= 75) %>%
  pull(district)  # Get the list of districts to remove for foreign_vis

# Remove rows from 'domestic_vis' where districts have >= 75% missing values
cleaned_domestic_vis <- domestic_vis %>%
  filter(!(district %in% districts_above_threshold_d))
sum(is.na(cleaned_domestic_vis$visitors))

# Remove rows from 'foreign_vis' where districts have >= 75% missing values
cleaned_foreign_vis <- foreign_vis %>%
  filter(!(district %in% districts_above_threshold_f))
sum(is.na(cleaned_foreign_vis$visitors))
```
```{r}
plot_before_after_NA <- function(data_with_na, data_without_na,main1=NULL) {
  # Histogram of visitors with NA values
  df_with_na <- ggplot(data = data_with_na, aes(x = visitors)) +
    geom_histogram(fill = "skyblue", color = "black", bins = 30, na.rm = FALSE) +
    labs(title = "Distribution of Visitors with Null Values", x = "Visitors") +
    theme_minimal() +ggtitle(main1) 
  
  # Histogram of visitors after removing NA values
  df_without_na <- ggplot(data = data_without_na, aes(x = visitors)) +
    geom_histogram(fill = "skyblue", color = "black", bins = 30, na.rm = TRUE) +
    labs(title = "Distribution of Visitors after removing Null Values", x = "Visitors") +
    theme_minimal() + ggtitle(main1)
  
  # Combine both histograms into a single plot using facets
  combined_plot <- cowplot::plot_grid(
    df_with_na + facet_wrap(~ "With Null Values"),
    df_without_na + facet_wrap(~ "Without Null Values"),
    ncol = 2
  )
  
  # Display the combined plot
  print(combined_plot)
}

# Example usage of the function with your dataframes
plot_before_after_NA(domestic_vis, cleaned_domestic_vis , "Distribution plot for domestic_visitors")
plot_before_after_NA(foreign_vis, cleaned_foreign_vis , "Distribution plot for foreign_visitors")

```

```{r}
total_rows_clean_d <- nrow(cleaned_domestic_vis)
total_rows_clean_f <- nrow(cleaned_foreign_vis)

total_missing_clean_d <- sum(is.na(cleaned_domestic_vis$visitors))
total_missing_clean_f <- sum(is.na(cleaned_foreign_vis$visitors))

percentage_missing_clean_d <- (total_missing_clean_d / total_rows_clean_d) * 100
percentage_missing_clean_f <- (total_missing_clean_f / total_rows_clean_f) * 100
# paste(percentage_missing_clean_d,"Remaining missing values for domestic_vis")
# paste(percentage_missing_clean_f,"Remaining missing values for foreign_vis")

```
#### But even after removing those districts with null values we have **`r round(percentage_missing_clean_d,2)`%** null values remaining.
#### Similarly even after removing those districts with null values we have **``r round(percentage_missing_clean_f,2)`%** null values remaining.

#### So we will impute the data with the Mean with respect to districts.
#### And then we will again plot distribution of data to make sure imputation doesn't change the distribution of original data.


```{r}
# mean_visitors_d <- mean(cleaned_domestic_vis$visitors, na.rm = TRUE)
# mean_visitors_f <- mean(cleaned_foreign_vis$visitors, na.rm = TRUE)
# 
# cleaned_domestic_vis$visitors[is.na(cleaned_domestic_vis$visitors)] <- mean_visitors_d
# cleaned_foreign_vis$visitors[is.na(cleaned_foreign_vis$visitors)] <- mean_visitors_f
# 
# imputed_data_d = cleaned_domestic_vis
# imputed_data_f = cleaned_foreign_vis

# imputed_data_d <- cleaned_domestic_vis %>%
#   group_by(district) %>%
#   mutate(visitors = ifelse(is.na(visitors), mean(visitors, na.rm = TRUE), visitors))
# 
# imputed_data_f <- cleaned_foreign_vis %>%
#   group_by(district) %>%
#   mutate(visitors = ifelse(is.na(visitors), mean(visitors, na.rm = TRUE), visitors))

# imputed_data_d <- cleaned_domestic_vis %>%
#   group_by(district, year) %>%
#   mutate(visitors = ifelse(is.na(visitors), mean(visitors, na.rm = TRUE), visitors))
# 
# imputed_data_f <- cleaned_foreign_vis %>%
#   group_by(district, year) %>%
#   mutate(visitors = ifelse(is.na(visitors), mean(visitors, na.rm = TRUE), visitors))

imputed_data_d <- cleaned_domestic_vis %>%
  group_by(district) %>%
  mutate(visitors = ifelse(is.na(visitors), round(mean(visitors[year == 2017], na.rm = TRUE)), visitors))

imputed_data_f <- cleaned_foreign_vis %>%
  group_by(district) %>%
  mutate(visitors = ifelse(is.na(visitors), round(mean(visitors[year == 2017], na.rm = TRUE)), visitors))


plot_before_after_NA(cleaned_domestic_vis , imputed_data_d ,"Distribution for Imputed Domestic_vis")
plot_before_after_NA(cleaned_foreign_vis , imputed_data_f , "Distribution for Imputed Foreign_vis")

```

```{r}
total_missing_values_d <- sum(is.na(imputed_data_d$visitors))
paste(total_missing_values_d, "null values in domestic_vis")
domestic_vis = imputed_data_d


total_missing_values_f <- sum(is.na(imputed_data_f$visitors))
paste(total_missing_values_f, "null values in foreign_vis")
foreign_vis = imputed_data_f

```


# Data Analysis
### Top 10 Districts with highest visitors
```{r}

#Creating a function to get top 10 districts and bar plot 
top_10_districts =function( visitors_df,type="domestic"){
  
  # Group by district, calculate the sum of visitors, and select the top 10 districts

  top_10_districts_df <- visitors_df %>%
  group_by(district) %>%
  summarise(total_visitors = sum(visitors,na.rm = T)) %>%
  arrange(desc(total_visitors)) %>%
  head(10)
  
  # convert into million on for domestic visitors
  if (type=="domestic"){
    top_10_districts_df$total_visitors <- top_10_districts_df$total_visitors / 1000000

  }
  
  bar_plot =ggplot(top_10_districts_df, aes(x = reorder(district,-total_visitors), y = total_visitors)) +
  geom_bar(stat = "identity", fill = "skyblue",color='black') +
  # scale_y_continuous(labels = scales::comma) +
  labs(title = "Top 10 Districts by Total Domestic Visitors", 
          x = "District", y = "Total Visitors (in Millions)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

  
  return( list("df"= top_10_districts_df,"bar_plot"=bar_plot))
}
dom_top_10_dis = top_10_districts(domestic_vis)
print(dom_top_10_dis$bar_plot)

fore_top_10_dis = top_10_districts(foreign_vis,type="foreign")
print(fore_top_10_dis$df)


```
### Top and Bottom 3 CAGR districts for domestic visitors

```{r}
total_vis_year <- domestic_vis %>%
  group_by(district, year) %>%
  summarise(visitors = sum(visitors, na.rm = T))

# Get unique districts for the year 2016
districts <- domestic_vis %>%
  filter(year == 2016) %>%
  select(district) %>%
  distinct() %>%
  pull()

# Function to calculate CAGR
calculate_cagr <- function(district_name) {
  fv <- total_vis_year %>% filter(district == district_name & year == 2019) %>% pull(visitors)
  pv <- total_vis_year %>% filter(district == district_name & year == 2016) %>% pull(visitors)


  if ( pv != 0) {
    cagr <- ((fv/pv)^(1/3) - 1) * 100
    return(c(district = district_name, cagr = round(cagr,2)))
  } else {
    return(c(district = district_name, cagr = 0) )
  }
}

# Apply the function to each district
cagr_list <- map_df(districts, calculate_cagr)

# Create a data frame from the list
district_cagr <- as.data.frame(cagr_list)
district_cagr$cagr = as.numeric(district_cagr$cagr)

# Get top and bottom 3 districts by CAGR
top3_districts_cagr <- district_cagr %>% arrange(desc(cagr)) %>% slice_head(n = 3)
bottom3_districts_cagr <- district_cagr %>% arrange(cagr) %>% slice_head(n = 3)

# Print the results
```
##### Top 3 Districts by CAGR:
```{r echo=F} 
print(top3_districts_cagr)

ggplot(top3_districts_cagr, aes(x= reorder(district,-cagr),y=cagr))+
  geom_bar(stat='identity',fill='lightgreen',color='black')+
  labs(x='District',y='CAGR') +
    geom_text(aes(label = paste0(cagr,'%')), vjust = -0.5, color = "black", size = 5) +

    theme_minimal() +
  theme(panel.grid.minor = element_blank()) # Remove grid lines


```

##### Bottom 3 Districts by CAGR:
```{r echo=F} 
print(bottom3_districts_cagr)
ggplot(bottom3_districts_cagr, aes(x= reorder(district,cagr),y=cagr))+
  geom_bar(stat='identity',fill='#f1807e', color='black')+
  labs(x='District',y='CAGR') +
    geom_text(aes(label = paste0(cagr,'%')), vjust = -0.5,hjust=-0.2, color = "white", size = 5) +

    theme_minimal() +
  coord_flip() +
  theme(panel.grid.minor = element_blank()) # Remove grid lines
```

### Peak and Low Season for Hyderabad District

```{r}
month_wise_hyb = function(vis_df){
  
  month_wise_hyb_df <- vis_df %>%
  filter(district == 'Hyderabad') %>%
  group_by(district, month) %>%
  summarize(visitors = sum(visitors))
  
  month_with_max_vis <- month_wise_hyb_df %>%
  filter(visitors == max(visitors))
  
  month_with_min_vis <- month_wise_hyb_df %>%
  filter(visitors == min(visitors))
  
  return (list('df'=month_wise_hyb_df, 'max_vis'=month_with_max_vis, 'min_vis'=month_with_min_vis))
  
}

month_wise_hyb_dom <- month_wise_hyb(domestic_vis)
month_wise_hyb_fore <- month_wise_hyb(foreign_vis)

# Find the month with the maximum visitors
month_with_max_vis_dom <- month_wise_hyb_dom$max_vis
month_with_max_vis_fore <- month_wise_hyb_fore$max_vis

# Find the month with the minimum visitors

month_with_min_vis_dom <- month_wise_hyb_dom$min_vis
month_with_mix_vis_fore <- month_wise_hyb_fore$min_vis
```

```
Month with highest domestic visitors `r month_with_max_vis_dom$month` , visitors: `r round(month_with_max_vis_dom$visitors / 1000000,3)` Million

Month with lowest Domestic visitors  `r month_with_min_vis_dom$month`, visitors: `r month_with_min_vis_dom$visitors`


Month with highest Foreign visitors `r month_with_max_vis_fore$month` , visitors: `r round(month_with_max_vis_fore$visitors / 1000000,3)` Million

Month with lowest Foreign visitors  `r month_with_mix_vis_fore$month`, visitors: `r month_with_mix_vis_fore$visitors`
```

```{r}
# Create a mapping of month names to numeric values
month_mapping <- c("January" = 1, "February" = 2, "March" = 3, "April" = 4,
                   "May" = 5, "June" = 6, "July" = 7, "August" = 8,
                   "September" = 9, "October" = 10, "November" = 11, "December" = 12)

# Use dplyr to create a new numeric 'month_num' column
month_wise_hyb_dom <- month_wise_hyb_dom$df %>%
  mutate(month_num = match(month, names(month_mapping)))

month_wise_hyb_fore <- month_wise_hyb_fore$df %>%
  mutate(month_num = match(month, names(month_mapping)))

# Create the time series plot using 'month_num' as x-axis
dom_plot =ggplot(month_wise_hyb_dom, aes(x = month_num, y = visitors)) +
  # geom_line() +
  geom_line() +
  geom_point(alpha=1) +
  labs(title = "Total Monthly Domestic Visitors in Hyderabad",
       x = "Month",
       y = "Visitors") +
  scale_x_continuous(breaks = 1:12, labels = names(month_mapping)) + # Customize x-axis labels
  theme_minimal() +
  theme( axis.text.x = element_text(angle = 45, hjust = 1) )

fore_plot = ggplot(month_wise_hyb_fore, aes(x = month_num, y = visitors)) +
  geom_line() +
  geom_point(alpha=1) +
  labs(title = "TOtal Monthly Foreign Visitors in Hyderabad",
       x = "Month",
       y = "Visitors") +
  scale_x_continuous(breaks = 1:12, labels = names(month_mapping)) + # Customize x-axis labels
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



print(dom_plot)
print(fore_plot)

```


### Year wise monthly trends of Top Districts
```{r}

month_wise_year_plot = function(vis_df, district_name) {
  month_wise <- vis_df %>%
    filter(district == district_name) %>%
    group_by(district, month, year) %>%
    summarize(visitors = sum(visitors,na.rm=T))
  
  # Create a mapping of month names to numeric values
  month_mapping <- c("January" = 1, "February" = 2, "March" = 3, "April" = 4,
                     "May" = 5, "June" = 6, "July" = 7, "August" = 8,
                     "September" = 9, "October" = 10, "November" = 11, "December" = 12)
  
  # Use dplyr to create a new numeric 'month_num' column
  month_wise <- month_wise %>%
    mutate(month_num = match(month, names(month_mapping)))
  
  plot = ggplot(month_wise, aes(x = month_num, y = visitors, group = factor(year), color = factor(year))) +
    geom_line() +
      geom_point(alpha=1) +
    labs(title = paste("Monthly Trendline of Visitors of ", district_name),
         x = "Month",
         y = "Number of Visitors",
         color = "Year") +
    scale_x_continuous(breaks = 1:12, labels = names(month_mapping)) +  # Customize x-axis labels
    theme_minimal() + 
    theme( axis.text.x = element_text(angle = 45, hjust = 1) )

  return (plot)
}
  hyd_dom_plot = month_wise_year_plot(domestic_vis, "Hyderabad")
  hyd_fore_plot = month_wise_year_plot(foreign_vis, "Hyderabad")
  hyd_dom_plot
  hyd_fore_plot
  
  mancherial_dom_plot = month_wise_year_plot(domestic_vis, "Mancherial")
  mancherial_dom_plot
  
```
  

### Top and Bottom 3 district in terms of domestic to foreign tourist raito
```{r}

# Merge data frames on 'district', 'date', 'month', and 'year'
dom_for_v <- inner_join(domestic_vis, foreign_vis, by = c('district', 'date', 'month', 'year'))

# Rename columns if needed
dom_for_v <- rename(dom_for_v, domestic_vis = visitors.x, foreign_vis = visitors.y)

# Group by 'district' and calculate the sum of 'domestic_vis' and 'foreign_vis'
dom_for_v_dis_sum <- dom_for_v %>%
  group_by(district) %>%
  summarise(domestic_vis = sum(domestic_vis,na.rm=T), foreign_vis = sum(foreign_vis,na.rm=T))

# Remove rows where 'foreign_vis' is zero
dom_for_v_dis_sum <- dom_for_v_dis_sum %>% filter(foreign_vis != 0)

# Calculate the ratio of 'domestic_vis' to 'foreign_vis'
dom_for_v_dis_sum <- dom_for_v_dis_sum %>%  mutate(dom_foreign_ratio = domestic_vis / foreign_vis)

# Find the top 3 and bottom 3 districts based on 'dom_foreign_ratio'
bottom_3_districts <- dom_for_v_dis_sum %>% arrange(desc(dom_foreign_ratio)) %>% select(district, dom_foreign_ratio) %>%  slice_head(n = 3)  
top_3_districts <- dom_for_v_dis_sum %>% arrange(dom_foreign_ratio) %>% select(district, dom_foreign_ratio) %>% slice_head(n = 3)


print(bottom_3_districts)

ggplot(bottom_3_districts, aes(x= reorder(district, -dom_foreign_ratio),y=dom_foreign_ratio/1000000))+
  geom_bar(stat='identity') +
  labs( title = "Bottom 3 Districts ( Wrost domestic to foreign ratio)",
        x = "District",
        y = "Domestic to Foreign ratio (in Millions)")



print(top_3_districts)

ggplot(top_3_districts , aes(x= reorder(district, -dom_foreign_ratio),y=dom_foreign_ratio))+
  geom_bar(stat='identity') +
  labs( title = "Top 3 Districts ( Best domestic to foreign ratio)",
        x = "District",
        y = "Domestic to Foreign ratio")

```

### Population to Tourist footfall ratio
```{r}

population = read.csv('./population.csv')
head(population)


dom_for_v_dis_2019 = dom_for_v %>% filter(year == '2019')

dom_for_v_dis_sum_2019= dom_for_v_dis_2019 %>%
  group_by(district) %>%
  summarise(domestic_vis = sum(domestic_vis,na.rm=T), foreign_vis = sum(foreign_vis,na.rm=T))

data_with_population <- left_join(dom_for_v_dis_sum_2019, population, by = c('district'))



dom_for_v_dis_sum_pop <- data_with_population %>%  mutate(dom_foreign_sum = domestic_vis + foreign_vis)
dom_for_v_dis_sum_pop <- dom_for_v_dis_sum_pop %>% filter(dom_foreign_sum != 0)


dom_for_v_dis_sum_pop <- dom_for_v_dis_sum_pop %>%
                          mutate(dom_foreign_pop_ratio = dom_foreign_sum / Population_2019 )

dom_for_v_dis_sum_pop_top5 = dom_for_v_dis_sum_pop %>% select(district,dom_foreign_pop_ratio) %>%
                              arrange(desc(dom_foreign_pop_ratio)) %>%
                                slice_head(n = 5)

dom_for_v_dis_sum_pop_bottom5 = dom_for_v_dis_sum_pop %>% select(district,dom_foreign_pop_ratio) %>%
  arrange(dom_foreign_pop_ratio) %>%
  slice_head(n = 5)

dom_for_v_dis_sum_pop_top5
dom_for_v_dis_sum_pop_bottom5

ggplot(dom_for_v_dis_sum_pop_top5 , aes(x= reorder(district, -dom_foreign_pop_ratio),y=dom_foreign_pop_ratio))+
  geom_bar(stat='identity',fill='lightgreen',color='black') +
  labs( title = "Top 5 Districts ( Best tourists to population ratio)",
        x = "District",
        y = "Tourists to population ratio)")

ggplot(dom_for_v_dis_sum_pop_bottom5 , aes(x= reorder(district, -dom_foreign_pop_ratio),y=dom_foreign_pop_ratio))+
  geom_bar(stat='identity',fill='#ffcccb',color='black') +
  labs( title = "Bottom 5 Districts ( Best tourists to population ratio)",
        x = "District",
        y = "Tourists to population ratio)")

```

### Conclusion

##### Hyderabad
> Hyderabad is a major economic and cultural hub in South India, attracting a large number of domestic and foreign
tourists to its historical landmarks and business centers. Must visit places 

* Charminar
* Golconda Fort
* Qutb Shahi Tombs
* Ramoji Film City


##### Mancherial
> Mancherial has strong contributions from coal mining and diverse industrial development, along with a favourable  climate for agriculture and significant infrastructure

* Coal Mines and Singareni Collieries Company Limited (SCCL) areas
* Kawal Tiger Reserve
* Sri Satyanarayana Swamy Temple

##### Rajanna Sircilla 
> Rajanna Sircilla has high population to tourist footfall due to the handloom industry, Kargil Park, and the historical
Sircilla Fort, and high population.


* Sircilla Textile Park
* Sri Raja Rajeshwara Swamy Devasthanam
* Ananthagiri Fort

##### Mulugu
> Mulugu is a district with a high ratio of domestic tourists to foreign tourists, primarily due to its popularity as a  weekend getaway spot for locals and the presence of famous Hindu temples.


* Ramappa Temple
* Bogatha Waterfall
* Medaram Jathara


```{r}
```

[data_desc]: ./data_des.png "Data Description"
[telangana_intro]: ./telangana_intro.png "Telangana Intro"